|

### 2023-06-09 full-paper/paper.Rmd
paper: fix typos

Building energy simulation (BES) has become increasingly applied to assess
building performance under climate change and yield a more sustainable and
resilient design [@yassaghi2019overview]. Weather files form the boundary
conditions of BES and directly affect the results [@bhandari2012evaluation].
Therefore, it is necessary to use further weather data considering climate
change for the design and performance evaluation of new and existing buildings
[@picard2020robustness].

>>>>

Building energy simulation (BES) has become increasingly applied to assess
building performance under climate change and yield a more sustainable and
resilient design [@yassaghi2019overview]. Weather files form the boundary
conditions of BES and directly affect the results [@bhandari2012evaluation].
Therefore, it is necessary to use future weather data considering climate
change for the design and performance evaluation of new and existing buildings
[@picard2020robustness].
